Ecological network control

### 2018-06-14 paper/manuscript.Rmd
Structural stability figure
Move correlogram to supplementary materials

```{r fig-correlogram, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks. Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
drake::loadd(fig_correlation)
fig_correlation[[1]]
```

@@

>>>>

@@

```{r fig-structural-stability, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]]/2, fig.cap="Control capacity and "}
drake::loadd(fig_structural_stability)

fig_structural_stability[[1]]
```

### 2018-06-14 paper/supp-info.Rmd
Move correlogram to supplementary materials

>>>>

```{r fig-correlogram, fig.width=fig_sizes()[[1]], fig.height=fig_sizes()[[1]], fig.cap="Mean Spearman correlation coefficients between control metrics (control capcity $\\phi$ and the likelyhood of being a superior node $\\sigma$) and centrality metrics commonly used to estimate a species' 'keystoness' (closeness centrality $l$ , betwenness $w$, eigen centrality $e$, page rank $g$ and degre $k$) in each of the networks. Purple and orange tiles indicate a positive correlation or negative correlation respectively."}
drake::loadd(fig_correlation)
fig_correlation[[1]]
```
